\documentclass[11pt]{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
%\usepackage{tgschola} % or any other font package you like

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname\quad
  \textcolor{blue}{\itshape\yourweb}\quad
  \textcolor{black}{\youremail}}

\newcommand{\soptitle}{Executive Summary}
\newcommand{\yourname}{Ana Paula Centeno}
\newcommand{\youremail}{anapaula@cs.rutgers.edu}
\newcommand{\yourweb}{https://www.cs.rutgers.edu/\~{}anapaula}

\newcommand{\statement}[1]{\par\medskip
  \underline{\textcolor{blue}{\textbf{#1:}}}\space
}

\usepackage[
  colorlinks,
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\begin{document}

\begin{center}\LARGE\soptitle\\
\large \yourname\ - February 2020
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt

\bigskip
\bigskip

At Rutgers I have become more than a professor, I became a role model
that instills a sense of belonging to female students and a mentor
that fosters interest for computer science.  Following are the main
points for this evaluation:

\bigskip

\begin{itemize}

  \item I have been instrumental in the complete redesign of the CS
    111 curriculum, as part of an effort that has been directly
    supported by the Rutgers Chancellor's Office.

  \item I have been one of the {\bf leaders in the CS/DIMACS Living
    Learning Community that has brought in \$490K from the Gates
    Foundation} through the Khoury Center for Inclusive Computing at
    Northeastern University. 
    
  \item As the Advancing Women in Computer Science {\bf coordinating
    committee leader} at Rutgers I am responsible for coordinating
    curricular revisions and co-curricular programming. 

%    we move on to tackle the redesign of
%    CS112, CS205 and CS206 to create continuity within our courses and
%    build students confidence and the co-curriculum activities already started on Fall 2020.

  \item CS111 course coordinator responsible for synchronized course
    content across lectures, the organization of 30 Learning
    Assistants and 30 graders. CS111 current enrollment is 2000
    students per Academic Year.

  \item Mentored an undergraduate student during development of a
    student-focused, goal oriented, recitation management platform
    (Dynamic Recitation) that is currently being used in CS111.
    
  \item Continue to volunteer as an academic advisor since Fall
    2016. I devote 3 hours a week to academic advising, on many days I
    see more than 15 students per hour. There is no course load relief
    for this work.

  \item My course workload per academic year has been:
    \subitem 2017/18: 5 classes + CS294 seminar 
    \subitem 2018/19: 4 classes + CS294 seminar

  \item Volunteer as a judge for HackHERS that takes place on
    weekends.

  \item High student ratings: considering the reviews for both courses
    my weighted mean for each question presented to the students is
    higher than the corresponding department's weighted mean.
  
\end{itemize}

\end{document}
