\documentclass[11pt]{article}
%\usepackage[letterpaper,text={5.5in,9in},left=1.9in,centering]{geometry} % margins
\usepackage{fullpage} %change the margins

\begin{document}

\title{Ana Paula Centeno \\ Information for Merit-based Raise Evaluation\vspace{-3ex}}
\date{February 2017}
\maketitle
\thispagestyle{empty} %suppress page number on this page

\section*{}
Teaching was always appealing to me but once I joined the Computer
Science Department and started engaging with students, I became more
than a professor, I became a role model and a mentor to my
students. My goal is for my students to understand the material
deeply; to that end, I strive to make learning enjoyable and instill
appreciation for what it means to be a computer scientist. Following
are the main points for this evaluation:

%When I joined the CS department as a teaching faculty I expected to be
%just one more professor, instead I became a role model and a mentor
%for my students. My goal is to make learning enjoyable and instill
%appreciation for Computer Science. Following are the main points for this
%evaluation:

\begin{itemize}
\item High student ratings: considering the reviews for CS112, my
  weighted mean for each question presented to the students is higher
  than the corresponding department's weighted mean. For CS111 my
  ratings are on par with the department's weighted mean. Even when I
  taught CS211 as PTL my ratings were on par or higher with the
  department's weighted mean.
\item Teaching large classes of more than 150 students: in spite of
  the large classrooms, I am able to engage students and make the class
  highly interactive.
\item My course workload per academic year has been:
  \subitem 2015/16: 6 classes 
  \subitem 2016/17: 5 classes
\item Developed a set of slides for CS111 that has been shared with
  other instructors. I find it that it helps the students to review the
  material after class and to prepare for exams.
\item In the process of developing a set of slides for CS112.
\item Volunteering as an academic advisor since Fall 2016. I devote 4
  hours a week to academic advising. With the growing enrollment it
  has been a challenge for students to be able to register for CS
  classes, many days I see more than 12 students per hour. There is no
  course load relief for this work.
\item Volunteering as a judge for HackRU that takes place on weekends.
\item Participated on the NTT hiring process 2015/16.
\item Participating in an effort to improve CS111 coordination among
  instructors, as well as to improve the class syllabus, material, and
  overall student experience.
\end{itemize}

\end{document}
