\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Ana Paula Centeno}
\address{ Department of Computer Science \\ Rutgers University \\ Piscataway, NJ 08854  }
\address{ 732~$\cdot$~874~$\cdot$~3035 \\ anapaula@rutgers.edu }

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}
  
  \begin{rSection}{Experience at Rutgers University}{Fall 2014 - present}{}

  \begin{rSubsection}{Awards}{}{}{}
	\item Provost's Award for Excellence in STEM Diversity, 2021.
 \end{rSubsection}

  \begin{rSubsection}{Teaching}{}{}{}
    \item CS-LLC Great Ideas in Computer Science Seminar, Spring 2019 - present.
    \item Introduction to Computer Science, Fall 2015 - present.
    \item Data Structures, Fall 2015 - present.
    \item Computer Architecture, Fall 2014, Spring 2015.
  \end{rSubsection}

  \begin{rSubsection}{Proposals}{}{}{}
    \item MLiSS: A Machine Learning Student Behavior Model to Identify
      Struggling Students in Introductory CS Courses. August 2020. Not funded.
  \end{rSubsection}
  
  \begin{rSubsection}{Student Mentoring}{}{}{}
    \item {\em Computer Science Living and Learning Community Advisor}: the
      mentoring role to the CS-LLC includes one seminar per academic
      year and review sessions during exams, Fall 2018 - present.
    \item {\em SAS Mentor}, Fall 2018 - present.
    \item {\em Member of the CS Academic Advising Team}: this role
      includes 2 hours of academic advising to students per week,
      Spring 2016 - present.
    \item {\em HackHers and HackRU Judge}, Spring 2016 - present.
    \end{rSubsection}

     \begin{rSubsection}{Women in Computer Science Initiative}{}{}{}
    \item Member of Rutgers Women in Computer Science Initiative partnership
      between DIMACS, the Department of Computer Science, and the
      Douglass Residential College aimed at increasing the percentage of
      undergraduate women majoring and minoring in Computer Science at
      Rutgers and elsewhere.
    \item Head of coordinating committee.
     \end{rSubsection}
    
     \begin{rSubsection}{Academic Administrative Activities}{}{}{}
     \item Team lead for the {\em modernization and standardization} of the
       Data Structures course, Fall 2020.
     \item {\em Coordinator of the Data Structures course}:
      responsible for the (a) organization of lecture and recitation
      material, assignments and exams, (b) coordination of 20 Learning
      Assistants, 20 tutors and 10 graders, and (c) exam coordination, Spring 2021 - present.
    \item Team lead for the {\em modernization and standardization} of the
      Introduction to Computer Science course, Summer 2019.
    \item {\em Coordinator of the Introduction to Computer Science course}:
      responsible for the (a) organization of lecture and recitation
      material, assignments and exams, (b) coordination of 30 Learning
      Assistants and 30 graders, and (c) exam coordination, Spring 2018 - Spring 2021.
    \end{rSubsection}

    \begin{rSubsection}{Student Advising and Research}{}{}{}
      \item {\em Member of the CS Education Research group}: modeling
        of struggling students.
      \item {\em Dynamic Recitation}: advised undergraduate student
        during development of a student-focused, goal oriented,
        recitation management platform.
    \end{rSubsection}
  \end{rSection}

  
\begin{rSection}{Education}
  \begin{rSubsection}{}{}{}{}
  \item {\bf Ph.D.}, Computer Science, Rutgers University, Piscataway, NJ 2019
  \item {\bf M.S.}, Computer Science, Stony Brook University, Stony Brook, NY, 2003.
  \item {\bf M.S.}, Computer Science, Federal University of Rio Grande do Sul, Porto Alegre, RS, Brazil, 1999.
  \item {\bf B.S.}, Computer Science, Catholic University of Pelotas, Pelotas, RS, Brazil, 1997.
  \end{rSubsection}
\end{rSection}

\end{document}
