\documentclass[11pt]{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
%\usepackage{tgschola} % or any other font package you like

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname\quad
  \textcolor{blue}{\itshape\yourweb}\quad
  \textcolor{black}{\youremail}}

\newcommand{\soptitle}{Executive Summary for Workload Assignment 2021-2022}
\newcommand{\yourname}{Ana Paula Centeno}
\newcommand{\youremail}{anapaula@cs.rutgers.edu}
\newcommand{\yourweb}{https://www.cs.rutgers.edu/\~{}anapaula}

\newcommand{\statement}[1]{\par\medskip
  \underline{\textcolor{blue}{\textbf{#1:}}}\space
}

\usepackage[
  colorlinks,
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\begin{document}

\begin{center}\LARGE\soptitle\\
\large \yourname\ - November 2020
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt

\bigskip
\bigskip

I would like to have my course load for AY20-21 reduced to 3 courses
and 1 seminar. Fall 2021 (CS112 and CS294), Spring 2022 (CS111 and
CS112).  Following are the projects that I am involved in the
department:

\bigskip

\begin{itemize}

  \item Continuation of CS111 redesign, as part of an effort that has
    been directly supported by the Rutgers Chancellor's Office.

  \item Started CS112 redesign on Fall 2020. Spring 21 will be the
    first iteration of the newly redesigned course.

  \item CS111 course coordinator responsible for synchronized course
    content across lectures, the organization of 30 Learning
    Assistants and 30 graders. CS111 current enrollment is 2000
    students per Academic Year.

  \item On Spring 2021 I will also coordinate CS112.

  \item I have been one of the {\bf leaders in the CS/DIMACS Living
    Learning Community that has brought in \$490K from the Gates
    Foundation} through the Khoury Center for Inclusive Computing at
    Northeastern University.

  \item {\bf PI of a NSF} proposal submitted on August 2020 (not funded) -
    MLiSS: A Machine Learning Student Behavior Model to Identify
    Struggling Students in Introductory CS Courses.
    
  \item As the Advancing Women in Computer Science {\bf coordinating
    committee leader} at Rutgers I am responsible for coordinating
    curricular revisions and co-curricular programming.
    
  \item Mentored two undergraduate students during Fall 2020
    development of a student-focused, goal oriented, recitation
    management platform (Dynamic Recitation) that is currently being
    used in CS111 and will be used in CS112 starting Fall 2020.
    
  \item Continue to volunteer as an academic advisor since Fall
    2016. There is no course load relief for this work.

  \item My course workload per academic year has been:
    \subitem 2018/19: 4 classes + CS294 seminar
    \subitem 2019/20: 4 classes + CS294 seminar
    \subitem Spring 21: Scheduled to teach two classes (CS111 and CS112).
  
\end{itemize}

\end{document}
