\documentclass[11pt]{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
%\usepackage{tgschola} % or any other font package you like

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname\quad
  \textcolor{blue}{\itshape\yourweb}\quad
  \textcolor{black}{\youremail}}

\newcommand{\soptitle}{Executive Summary for Workload Assignment 2022-2023}
\newcommand{\yourname}{Ana Paula Centeno}
\newcommand{\youremail}{anapaula@cs.rutgers.edu}
\newcommand{\yourweb}{https://www.cs.rutgers.edu/\~{}anapaula}

\newcommand{\statement}[1]{\par\medskip
  \underline{\textcolor{blue}{\textbf{#1:}}}\space
}

\usepackage[
  colorlinks,
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\begin{document}

\begin{center}\LARGE\soptitle\\
\large \yourname\ - October 2021
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt

\bigskip
\bigskip

I would like to have a course load for AY22-23 of 4 courses and 1 seminar so that I can continue focusing on diversity. Following are the projects that I am involved in the department:

\bigskip

\begin{itemize}

\item I have been leading introductory courses redesign. The redesign is part of an effort that has been directly supported by the Rutgers Chancellor's Strategic Initiative.

\begin{itemize}
  \item CS112 redesign started on Fall 2020; Spring 2021 had the
    first iteration of the newly redesigned course; Fall 2021 has first iteration of
    new assignments on real world applications.
   \item Continuation of CS111 assignments redesign.
\end{itemize}

  \item I have been the course coordinator responsible for synchronized lecture and recitation content, assignments and exams across lectures; Coordinator also organizes the Learning Assistants, graders, and tutors.
    \begin{itemize}
    	\item CS111 current enrollment is 1800 per academic year. Starting Fall 2021, Lars Sorensen
    will coordinate CS111, I am currently serving as an advisor.
    	\item CS112 current enrollment is 1300 per academic year.
      	\item Coordinated both CS111 and CS112 courses on Spring 2021.
      \end{itemize}
  
  \item I have been one of the {\bf leaders in the CS/DIMACS Living
    Learning Community that has brought in \$490K from the Gates
    Foundation} through the Khoury Center for Inclusive Computing at
    Northeastern University.

  \item Initiated a tutoring program for CS111/CS112 students
    supported by the Gates Foundation Grant. There are currently 20
    tutors per semester for both courses.
  
  \item Started research to qualify and quantify the diversity focused initiatives that have been deployed in our department.
    
  \item {\bf PI of a NSF} proposal submitted on August 2020 (not funded) -
    MLiSS: A Machine Learning Student Behavior Model to Identify
    Struggling Students in Introductory CS Courses.
    
  \item As the Advancing Women in Computer Science {\bf coordinating
    committee leader} at Rutgers I am responsible for coordinating
    curricular revisions and co-curricular programs.
    
  \item Mentored two undergraduate students during Fall 2020
    development of a student-focused, goal oriented, recitation
    management platform (Dynamic Recitation) that is currently being
    used in CS111 and CS112.
    
  \item Continue to volunteer as an academic advisor since Fall
    2016. There is no course load relief for this work.

  \item My course workload per academic year has been:
    \subitem 2019/20: 4 classes + CS294 seminar
    \subitem 2020/21: 3 classes + CS294 seminar
  
\end{itemize}

\end{document}
 